Reanalysis Step 3: Comprehensive Imputation Diagnostics

### 2025-08-30 reanalysis-3-imputation_diagnostics.qmd
clean up diagnsotics

# Calculate imputed correlation (first imputation)
bilateral_imp <- imputed_datasets[[1]] |>
  filter(e_mrn_deidentified %in% bilateral_ids) |>
  group_by(e_mrn_deidentified) |>
  arrange(row_number()) |>
  mutate(eye = paste0("eye", row_number())) |>
  ungroup() |>
  select(e_mrn_deidentified, eye, outcome_VA_logMAR) |>
  pivot_wider(names_from = eye, values_from = outcome_VA_logMAR)

cor_outcome_imp <- cor(bilateral_imp$outcome_VA_logMAR_eye1, bilateral_imp$outcome_VA_logMAR_eye2, use = "complete.obs")

@@

# Visualization
p_bilateral <- ggplot(bilateral_imp, aes(x = outcome_VA_logMAR_eye1, y = outcome_VA_logMAR_eye2)) +
  geom_point(alpha = 0.4, color = "#2E86AB") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "red") +
  labs(
    title = sprintf("Between-Eye Correlation After 2l.pan Imputation (r = %.3f)", cor_outcome_imp),
    x = "Eye 1 Outcome VA (logMAR)",
    y = "Eye 2 Outcome VA (logMAR)"
  ) +
  theme_minimal()

print(p_bilateral)
```

>>>>

# Calculate imputed correlation (first imputation)
bilateral_imp <- imputed_datasets[[1]] |>
  filter(e_mrn_deidentified %in% bilateral_ids) |>
  group_by(e_mrn_deidentified) |>
  arrange(row_number()) |>
  mutate(eye = row_number()) |>
  ungroup() |>
  select(e_mrn_deidentified, eye, outcome_VA_logMAR) |>
  pivot_wider(names_from = eye, values_from = outcome_VA_logMAR, names_prefix = "outcome_eye")

# Check column names exist and calculate correlation
if ("outcome_eye1" %in% names(bilateral_imp) && "outcome_eye2" %in% names(bilateral_imp)) {
  cor_outcome_imp <- cor(bilateral_imp$outcome_eye1, bilateral_imp$outcome_eye2, use = "complete.obs")
} else {
  cor_outcome_imp <- NA
  warning("Expected columns not found in bilateral_imp")
}

@@

# Visualization (only if correlation was calculated)
if (!is.na(cor_outcome_imp)) {
  p_bilateral <- ggplot(bilateral_imp, aes(x = outcome_eye1, y = outcome_eye2)) +
    geom_point(alpha = 0.4, color = "#2E86AB") +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
    geom_smooth(method = "lm", se = TRUE, color = "red") +
    labs(
      title = sprintf("Between-Eye Correlation After 2l.pan Imputation (r = %.3f)", cor_outcome_imp),
      x = "Eye 1 Outcome VA (logMAR)",
      y = "Eye 2 Outcome VA (logMAR)"
    ) +
    theme_minimal()

  print(p_bilateral)
} else {
  cat("Between-eye correlation plot could not be generated.\n")
}
```
